Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-24 main.tex
:lipstick: Update layout plots
:pencil: Update configuration

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$. $d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is assumed across transmit antennas and IRS elements. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n^2=-40\,\si{\dBm}$ at all subbands as reference. We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$. We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.

		% (denotes the proportion allocated to the multisine waveform) (denotes the proportion used for energy harvesting)
		% The R-E boundary is a segment between the WIT point and the WPT point.
		% where the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform and the splitting ratio $\rho$ denotes the proportion used for energy harvesting. The R-E region is characterized under different $\delta$ and $\rho$ from \num{0} to \num{1}.

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
		\end{subsection}

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$). The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively). To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS. In contrast to Remark~\ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for $NL$ variables in total. When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-UE channel to the AP-UE channel at all subbands, namely
		\begin{equation}
			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\mathrm{D},n}/h_{\mathrm{I},n,l}h_{\mathrm{R},n,l}\right)}},\quad \forall n,l.
		\end{equation}
		\textit{First}, it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions. \textit{Second}, the performance of all four IRS strategies coincide with each other for narrowband SWIPT. It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region. Therefore, for a given channel, we can fix the active and passive beamforming, and only adapt the waveform and splitting ratio to achieve different R-E performance. This is because when the bandwidth is small, all channels are approximately flat such that the optimal ideal reflection coefficients at all subbands are approximately the same. Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies. \textit{Third}, a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT. Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution. By adaptive passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power. The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.
	\end{section}

>>>>

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we suppose a layout as Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}. For the algorithms, the tolerance is $\epsilon=10^{-8}$, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, and we assume $\delta=\rho$ for simplicity. All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis has been normalized to per-subband rate $R/N$.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the average R-E region under different IRS configuration for narrowband transmission ($B=1\,\si{\MHz}$) and broadband transmission ($B=10\,\si{\MHz}$). The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively). To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS. In contrast to Remark~\ref{re:irs_frequency_flat}, each element in the ideal FS IRS is assumed to have an independent reflection coefficient for each subband, accounting for $NL$ variables in total. When there is only one transmit antenna, each ideal IRS element simply aligns the AP-IRS-UE channel to the AP-UE channel at all subbands, namely
		\begin{equation}
			\theta_{l,n}^{\star}=e^{j\arg{\left(h_{\mathrm{D},n}/h_{\mathrm{I},n,l}h_{\mathrm{R},n,l}\right)}},\quad \forall n,l.
		\end{equation}
		\textit{First}, it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions. \textit{Second}, the performance of all four IRS strategies coincide with each other for narrowband SWIPT. It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region. Therefore, for a given channel, we can fix the active and passive beamforming, and only adapt the waveform and splitting ratio to achieve different R-E performance. This is because when the bandwidth is small, all channels are approximately flat such that the optimal ideal reflection coefficients at all subbands are approximately the same. Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies. \textit{Third}, a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT. Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution. By adaptive passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power. The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.
		\end{subsection}
	\end{section}
